### 2023-07-28 python_excel_ite.tex
draft done, needs final proofreading and editing

\ABSTRACT{%
TODO: Text of your abstract % Enter your abstract
}%

>>>>

\ABSTRACT{%
A staple of many spreadsheet based management science textbooks and courses are the use of Excel for activities such as model building, sensitivity analysis, goal seeking and Monte-Carlo simulation. What might those things look like if done with Python? We describe a teaching module in which Python is used to do typical Excel based modeling and data wrangling tasks. In addition, students are exposed to basic software engineering principles including project folder structures, version control, object oriented programming and other more advanced Python skills, creating deployable packages and documentation. The module is supported with Jupyter notebooks, Python scripts, course web pages which include numerous screencasts, and a few GitHub repositories. All of the supporting materials are permissively licensed and freely accessible.
}%
